Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-04-25 main.Rmd
small edits, and subjective wording/comments etc.

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(bookdown)
library(rticles)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(tsibble)
remotes::install_github("Sayani07/gravitas")
library(gravitas)
library(ggpubr)
library(xtable)
library(kableExtra)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
knitr::opts_knit$set(root.dir = here::here())
```

@@

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1))
kable(table_mayan,
      format = "latex",
      booktabs = TRUE,
      align = "l",
      caption = "Hierarchy table for Mayan calendar with all circular single-order-up granularities.") %>%
  kable_styling()
  #row_spec(0, bold = TRUE) %>%
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T)
```

@@

\begin{definition}\label{def:clash}
A {\bf harmony} is a pair of cyclic granularities that do not contain any missing combinations of its categories.
\end{definition}

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(bookdown)
library(rticles)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(tsibble)
if (requireNamespace("gravitas"))
  remotes::install_github("Sayani07/gravitas")
library(gravitas)
library(ggpubr)
library(xtable)
library(kableExtra)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
#knitr::opts_knit$set(root.dir = here::here())
```

@@

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1))
kable(table_mayan,
      format = "latex",
      booktabs = TRUE,
      align = "l",
      caption = "Hierarchy table for Mayan calendar with circular single-order-up granularities.") %>%
  kable_styling()
  #row_spec(0, bold = TRUE) %>%
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T)
```

@@

\begin{definition}\label{def:clash}
A {\bf harmony} is a pair of cyclic granularities that does not contain any missing combinations of its categories.
\end{definition}
